---
title: "Adj Norming Analysis"
author: "Natasha Vernooij"
date: "2/5/2022"
---

```{r}
Adjective_Norming_Data <- read.csv("/desktop/Adj Norming Data.csv")
View(Adjective_Norming_Data)          
```
```{r}
Adjective_Norming_Data$Subj_num <-factor(Adjective_Norming_Data$Subj_num)
Adjective_Norming_Data$Stimulus_list <-factor(Adjective_Norming_Data$Stimulus_list)
Adjective_Norming_Data$Span_acq_age <- as.numeric(Adjective_Norming_Data$Span_acq_age)
Adjective_Norming_Data$Eng_acq_age <- as.numeric(Adjective_Norming_Data$Eng_acq_age)
Adjective_Norming_Data$Percent_convo_w_bilinguals <- as.numeric(Adjective_Norming_Data$Percent_convo_w_bilinguals)
Adjective_Norming_Data$perc_time_EP <- as.numeric(Adjective_Norming_Data$perc_time_EP)
Adjective_Norming_Data$Age <- as.numeric(Adjective_Norming_Data$Age)
```
##Graphing
#Create the Subject means by the conditions (word order by type of adjective):
```{r}
library(dplyr)
subjmeans <-Adjective_Norming_Data %>%
  group_by(Subj_num, Word_order, Type_of_Adj) %>%
  dplyr::summarize(Mean = mean(Rating, na.rm=TRUE)) %>%
  ungroup()
```

```{r}
#optional: save subject means in .csv file
#write.csv(subjmeans,"/desktop/Subject Means.csv")
```

#Graph
#graph the subject means- error bars are standard error
```{r}
library(ggplot2)
Adj_Norming_graph <- ggplot(subjmeans, aes(Word_order, Mean, col=Type_of_Adj))+
  scale_y_continuous(limit= c(1,7), expand = c(0,0)) + scale_x_discrete(expand = c(.25,0)) +
  stat_summary(fun.data="mean_se", position=position_dodge(width=.15), size= 1) +
  stat_summary(aes(group=Type_of_Adj),fun.data="mean_se", geom="line", size= 1,
  position=position_dodge(width=.15))+
  labs(col="Adjective Type", y= "Mean Rating", x= "Word Order") +
  theme_bw() + 
  theme(text = element_text(size = 20)) 
Adj_Norming_graph
```

##T-tests
Test the differences between the word order for each adjective type: 
Change: adjectives that change position and change meaning depending on their location:
There is a significant difference between the positions, where bilinguals prefer these adjectives in the pre-nominal position, t(37)=3.14, p<.01. Mean difference= 0.39.
```{r}
t.test(Mean ~ Word_order, data=subjmeans[subjmeans$Type_of_Adj %in% c('change'),], paired=T)
```
No change: adjectives that are predominantly post-nominal and don't change meaning:
There is a significant difference between the positions, where bilinguals prefer these adjectives in the post-nominal position, t(37)=-7.13, p<.001. Mean difference= -2.11.
```{r}
t.test(Mean ~ Word_order, data=subjmeans[subjmeans$Type_of_Adj %in% c('no change'),], paired=T)
```

Post-nominal: adjectives that are mandatorily post-nominal:
There is a significant difference between the positions, where bilinguals prefer these adjectives in the post-nominal position, t(37)=-7.14, p<.001. Mean difference= -1.86.
```{r}
t.test(Mean ~ Word_order, data=subjmeans[subjmeans$Type_of_Adj %in% c('post-nominal'),], paired=T)
```

Pre-nominal: adjectives (quantifiers) that are mandatorily pre-nominal:
There is a significant difference between the positions, where bilinguals prefer these adjectives in the pre-nominal position, t(37)=11.81, p<.001. Mean difference= 2.99.
```{r}
t.test(Mean ~ Word_order, data=subjmeans[subjmeans$Type_of_Adj %in% c('pre-nominal'),], paired=T)
```

##Descriptive Stats
```{r}
summary(Adjective_Norming_Data)
```
n= 38; 2 did not finish whole survey
Age: 18-48, mean= 21
Gender: m=8 f=26, nb=1 prefer not to answer=1
LexTALE Eng: range= 52.24-96.22, mean= 78.87
LexTALE Esp: range= 43.74-95.08, mean= 66.33
% El Paso: range= 40-100, mean = 95.67
% talk with El Paso: range= 31-100, mean=88.64
Hispanic (Latinx?): y=33, n=3

##Item Means and SD
#calculate mean and sd for each appearance of an adjective in each position, include the type_of_adj column
```{r}
#na.rm=TRUE removes NA data points before calculating mean and sd
item_means <-Adjective_Norming_Data %>%
  group_by(item_adj, Word_order, Type_of_Adj) %>%
  summarize(item_mean = mean(Rating, na.rm=TRUE), item_SD=sd(Rating, na.rm=TRUE)) %>%
  ungroup()
View(item_means)
#calculate the number of times each adjective appears/how many data points are used to compute the mean and sd  
item_counts <- Adjective_Norming_Data %>% count(item_adj, Word_order)
```

```{r}
#Optional: save the item means as a .csv file then copy the counts into that file
write.csv(item_means,"/desktop/Item Means.csv")
```
